Social Visual Analytics: DevOps for Data Scientists

### 2015-03-24 paper.tex
working
yes
Renamed some files
cram in a ton of quotes - completely unedited and without narrative
better distinguish colors; comment; capitalize GitHub
abstract, teaser

%\usepackage{dblfloatfix}
%\usepackage{fixltx2e}
\usepackage{url}

@@

\title{RCloud: Integrated Visualization, Analysis, Development, and Deployment}

@@

%% Abstract section.
\abstract{ Consider the emerging role of a data science team within an
  organization. Individual data scientists and statisticians usually
  work on loosely related problems, and must devise effective ways to
  share their findings and move results from exploratory data analysis
  into automated diagnostics and reports deployed for wider consumption.
  There are two problems with the current
  practice. First, there are gaps in this workflow: EDA is performed
  with one set of tools, and automated reports and deployments with another.
  Second, EDA environments often assume a single-developer perspective,
  while data scientist teams would get much benefit from easier sharing
  of scripts and data feeds, experiments, annotations, and automated
  recommendations, which are well beyond what traditional version control
  systems provide. We contribute and justify the following three
  requirements for systems built to support current data science teams
  and users: \emph{technology transfer}, \emph{coexistence}, and
  \emph{discoverability}. In addition, we contribute the design and
  implementation of RCloud, a system that supports the requirements
  collaborative data analysis, visualization and web deployment. We
  discuss the design decisions, tradeoffs and limitations, and compare RCloud
  to other current proposals.
  \carlos{RCloud has been in production use for more than a year and has about one hundred active users. We will discuss the adoption issues and etc etc.}
} % end of abstract

@@

%% Uncomment below to include a teaser figure.
\teaser{
  \centering
  \includegraphics[width=.95\linewidth]{fig/teaser/teaser.pdf}
  % \vspace{-.5em}
  \caption{
    \carlos{Come up with caption for this. The story is: hackers/scripters work in the middle (and bottom-right), rest of organization has automatic access to their work on left and top-right.}
  }
% \vspace{-.5em}
}

@@

\input{introduction}
\input{relatedwork}
\input{system}
\input{casestudies}
\input{discussion}
\input{conclusion}

>>>>

%\usepackage{dblfloatfix}
%\usepackage{fixltx2e}
\usepackage{url}
\usepackage{scrextend}   % for addmargin in introduction.tex
\usepackage[usenames,dvipsnames]{xcolor}

@@

\title{Social Visual Analytics: DevOps for Data Scientists}

@@

%% Abstract section.
\abstract{ Consider the emerging role of data science teams embedded in
  larger organizations. Individual analysts work on loosely related problems,
  and must share their findings with each other and the organization at large,
  moving results from exploratory data analyses (EDA)
  into automated visualizations, diagnostics and reports deployed for wider consumption.
  There are two problems with the current
  practice. First, there are gaps in this workflow: EDA is performed
  with one set of tools, and automated reports and deployments with another.
  Second, these environments often assume a single-developer perspective,
  while data scientist teams would get much benefit from easier sharing
  of scripts and data feeds, experiments, annotations, and automated
  recommendations, which are well beyond what traditional version control
  systems provide. We contribute and justify the following three
  requirements for systems built to support current data science teams
  and users: \emph{technology transfer}, \emph{coexistence}, and
  \emph{discoverability}. In addition, we contribute the design and
  implementation of RCloud, a system that supports the requirements of
  collaborative data analysis, visualization and web deployment.
  The biggest deployment of RCloud has been in active use for more than a year,
  and has about fifty active users. We report on interviews with some of these users, and
  discuss the design decisions, tradeoffs and limitations, comparing RCloud
  to other current proposals.
} % end of abstract

@@

%% Uncomment below to include a teaser figure.
\teaser{
  \centering
  \includegraphics[width=.95\linewidth]{fig/teaser/teaser.pdf}
  % \vspace{-.5em}
  \caption{
    An overview of features in RCloud. RCloud was built to support an environment in which a large number of loosely-related problems in data and visual analytics are solved by a small number of \emph{hackers} and \emph{scripters}. In such a shared environment, \emph{discoverability} is also a problem. RCloud supports search, annotation, recommendation, and commenting for all notebooks, enabling an overview mode where users can \emph{browse} popular and recent analyses. When problems and data sources change constantly, deployment becomes a time sink; RCloud supports \emph{transparent and automatic} deployment of analyses as web pages and web services, allowing a seamless transition from exploratory work to production code.
  }
% \vspace{-.5em}
}

@@

\input{introduction}
\input{relatedwork}
\input{system}
\input{casestudies}
\input{interviews}
\input{discussion}
\input{conclusion}
